\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{hyperref}


\input{glyphtounicode}

% -------------------- FONT --------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \vspace{-4pt}
\end{flushright}

\vspace{-7pt}

\begin{center}
    \textbf{\Huge \scshape Mohamed Khater} \\ \vspace{8pt}
    \small 
    \faGithub
    \href{https://github.com/Mo-Khater}{\underline{github.com/Mo-Khater}} $  $
    \faEnvelope$  $
    \href{mailto:mk0015264@gmail.com}
    {\underline{mk0015264@gmail.com}}
    \faPhone$  $
    \underline{+201068071299}
    \faLinkedin$  $
    \href{https://www.linkedin.com/in/mohamed-khater-924782243/}{\underline{linkedin.com/in/mohamedkhater}} $  $
\end{center}

% -------------------- EDUCATION --------------------
\section{EDUCATION}
\begin{itemize}[leftmargin=0.15in, label={}]
    \normalsize{\item{
        \textbf{Cairo University}{ --- Bachelor of Computer Engineering} \\ 
        \textit{2021 - Present} | GPA: 3.7 | 2nd in class (2022-2023) \\ 
        Relevant Courses: Data Structures, Algorithms, Machine Learning, Operating Systems
    }}
\end{itemize}

% -------------------- SKILLS --------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Programming Languages}{: C++, Java, Python, Dart, JavaScript} \\
     \textbf{Web Development}{: React.js, Node.js, Express.js, SQL, MongoDB} \\
     
     \textbf{Mobile Development}{: Flutter, Firebase} \\

     \textbf{Problem-Solving}{: Algorithms, Data Structures, Competitive Programming} \\
     \textbf{Tools}{: Git, GitHub, Linux, REST APIs} \\
     
    }}
 \end{itemize}

% -------------------- EXPERIENCE --------------------
% \section{Professional Experience}
%   \resumeSubHeadingListStart

%         \resumeProjectHeading
%         {\textbf{Big Company} $|$ \footnotesize\emph{Software Engineer Intern}}{May 2024 -- August 2024}
%         \resumeItemListStart
%           \resumeItem{Bullet point 1}
%           \resumeItem{Bullet point 2}
%           \resumeItem{Bullet point 3}
%           \resumeItem{\textbf{\textit{TECH STACK: }}}
%         \resumeItemListEnd

%         \resumeProjectHeading
%         {\textbf{University of Central Florida} $|$ \footnotesize\emph{Undergraduate Teaching Assistant}}{January 2023 -- May 2024}
%         \resumeItemListStart
%           \resumeItem{Bullet point 1}
%           \resumeItem{Bullet point 2}
%           \resumeItem{Bullet point 3}
%         \resumeItemListEnd
 
%     \resumeSubHeadingListEnd 


% -------------------- PROJECTS --------------------
\section{PROJECTS}
\resumeSubHeadingListStart
    
    \resumeProjectHeading
    {\textbf{\href{https://github.com/TeleGrammy}{\underline{Telegram Application \faExternalLink}}} $|$ \footnotesize\emph{Flutter, Dart, Firebase}}{}
    \resumeItemListStart
        \resumeItem{Developed a feature-rich Telegram-like app using Flutter and Dart, fully integrated with a custom backend.}
        \resumeItem{Implemented multi-method authentication (email, Google, Facebook, GitHub) and secure real-time messaging with end-to-end encryption.}
        \resumeItem{Developed advanced group and channel management, including admin roles and permissions.}
        \resumeItem{Added privacy controls, media sharing, and push notifications for a seamless user experience.}
        \resumeItem{Designed a user-friendly admin dashboard for managing users and filtering inappropriate content.}
        \resumeItem{Ensured smooth backend communication with REST APIs for robust and scalable performance.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{\href{https://github.com/Roshdy23/Gate-Access-Controller}{\underline{License Plate Recognition System \faExternalLink }}} $|$ \footnotesize\emph{Python, Cv2}}{}
    \resumeItemListStart
        \resumeItem{Designed a system to automatically recognize license plates using both classic machine learning and deep learning techniques, comparing their performance.}
        \resumeItem{Applied image processing techniques to enhance plate visibility and extract characters.}
        \resumeItem{Implemented database verification for access authorization based on recognized license plates.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{\href{https://github.com/Mo-Khater/SearchEngine.git}{\underline{Search Engine \faExternalLink }}} $|$ \footnotesize\emph{Java, Algorithms}}{}
    \resumeItemListStart
        \resumeItem{Developed a search engine with a web crawler, indexer, and ranking algorithm for efficient keyword-based search results.}
        \resumeItem{Implemented crawling and indexing to store and retrieve web pages effectively.}
        \resumeItem{Designed a ranking algorithm to improve the relevance and accuracy of search results.}
    \resumeItemListEnd
        
\resumeSubHeadingListEnd

% -------------------- EXPERIENCE --------------------
\section{TRAINING \& CERTIFICATIONS}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Machine Learning and Data Science Training} --- ITI, 2024\\
    Covered Probability, Statistics, Supervised \& Unsupervised ML, and Intro to Deep Learning.}

    \resumeProjectHeading
    {\textbf{Flutter Bootcamp} --- Udemy, 2024\\
    30 hours: Advanced Dart and Flutter through 5 projects.}

    \resumeProjectHeading
    {\textbf{Node.js, Express.js \& MongoDB Bootcamp} --- Udemy, 2024\\
    42 hours: REST API, Authentication, Payment Integration.}   

\resumeSubHeadingListEnd 

\section{Achievements}
\resumeSubHeadingListStart
    \item - 2nd in class (2022-2023) with a GPA of 3.7.
    \item - Completed 10+ projects in mobile and web development.
    \item - Led a 10-person team to develop a full website for TCCD.
    \item - Solved 400+ algorithm problems on LeetCode.
\resumeSubHeadingListEnd


\end{document}